---
title: "IRSAE **R** workshop"
subtitle: "Climate Change Ecology"
author: "Lars Dalby"
date: "`r format(Sys.Date())`"
output:
  xaringan::moon_reader:
    lib_dir: libs
    css: ["default", "default-fonts"]
    nature:
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
---

```{r setup, include=FALSE}
options(htmltools.dir.version = FALSE)
```

# Program

Not much time, but here are the topics I think we should touch upon:

--

- Useful features of the RStudio IDE

- Advice on project management

- RMarkdown

- The Tidyverse

- Maps

- Random stuff that come up over the next couple of hours 

---

# RStudio IDE

Nearly everybody uses RStudio (and I strongly recommed using it)

Let's have a look around - live demo

---

# Projects

## Use a project-oriented workflow

--

Why?

--

Makes these things easier:

- Working on multiple projects at the same time
- Starting and stopping
- Collaborating

--

How?

--

- Have a directory dedicated to your project
- Create an RStudio project
- (make this a git repo)

---

# What are the benefits of `.rproj`?

--

- RStudio rembers settings, open files, unsaved files(!), etc
- Dedicated instance of RStudio
- Dedicated `R` process
- File browser is looking the right place
- Work directory starts at the right place


.footnote[
See Jenny Bryan's [article](https://www.tidyverse.org/articles/2017/12/workflow-vs-script/) on Project-oriented workflows for more details
]

---

You can now safely remove these lines:

```{r eval=FALSE, tidy=FALSE}
setwd("/Users/Lars/path/to/secret/place")
rm(list = ls())
```

